---
title: "Homework 2"
author: "Junhan Huang"
date: "2/10/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nycflights13)
library(ggplot2)
library(dplyr)
library(magrittr)
```

# 1.Problem 1

```{r}
F<-flights
```

## 1.1 How many flights have a missing dep_time?

```{r}
Missing<-F%>%filter(is.na(dep_delay))
dim(Missing)[1]
```

There are 8255 flights have a missing dep_time

## 1.2 What other variables are missing?
```{r}
n1<-dim(F)[2]
int1<-1:n1
list<-c()

for (i in int1) {
  
  Missing<-which(is.na(F[,i])==TRUE)
  LM<-length(Missing)
  
  if (LM!=0){
    list[i]=i
  }
  else{
   list[i]=0
 }
}

CN<-colnames(F)
CN[list]
```

There are 5 variables having missing value, which are "dep_time", "dep_delay", "arr_time", "arr_delay", "tailnum", and "air_time" 


## 1.3 What might these rows represent?

These rows might represent the flights were canceled

# 2. Problem 2
```{r}
dpt<-as.character(F$dep_time)
scht<-as.character(F$sched_dep_time)
new_dpt<-c()
new_scht<-c()

n2<-length(dpt)
int2<-1:n2

for(i in int2){
  sp<-strsplit(dpt[i], split = "")
  sp<-sp[[1]]
  if(length(sp)==3){
    new_dpt[i]<-paste(sp[1],":",sp[2],sp[3],sep = "")
  }
  else if(length(sp)==4){
    new_dpt[i]<-paste(sp[1],sp[2],":",sp[3],sp[4],sep = "")
  }
  else{
    new_dpt[i]=NA
  }
}

for(i in int2){
  sp<-strsplit(scht[i], split = "")
  sp<-sp[[1]]
  if(length(sp)==3){
    new_scht[i]<-paste(sp[1],":",sp[2],sp[3],sep = "")
  }
  else if(length(sp)==4){
    new_scht[i]<-paste(sp[1],sp[2],":",sp[3],sp[4],sep = "")
  }
  else{
    new_scht[i]=NA
  }
}

F$dep_time<-new_dpt
F$sched_dep_time<-new_scht

write.csv(F, "New Flights.csv")

```

# 3. Problem 3

```{r}
F %>% group_by(month, day) %>%
  summarize(A_D_D= mean(dep_delay, na.rm = TRUE),
            PC= sum(is.na(dep_time)/n())) %>%
  ggplot(mapping = aes(x = A_D_D, y = PC)) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE)

```

From the plot, we can say there is a patterm and the proportion of cancelled flights is related to the average delay
